Extended Data

### 2021-10-21 doc/manuscript/Dow_manuscript_Nature.Rmd

![**Figure 3 | Sensitivity of annual growth, as derived from tree-rings, to monthly maximum temperatures, for `r n_chronologies` chronologies from `r n_cores_sites` sites across eastern North America** (`r EDF_map `). Chronologies are grouped by xylem porosity and ordered by mean maximum April temperature. Chronology details are given in the Supplementary Information.](tables_figures/tree_rings_tmax.png){ width=100% }

@@

<!--QUILT PLOT METHODS-->
Correlations between monthly climate and $RWI$ were assessed using ‘dplR’[@bunn_dendrochronology_2008] and ‘bootRes’[@zang_dendroclimatic_2013] in R v.1.3.1093 (R Core Team, 2020), which correlated functions and bootstrapped confidence intervals for these relationships[@biondi_dendroclim2002_2004].
We analyzed these correlations for January through September of the current year (presented in Fig. `r tree_rings`, `r EDF_tree_rings_TMIN`).
To test for potential lag effects effects of spring temperatures on the following year's growth, we also ran a version of the analysis extending back to include climate of every month of the previous year (`r EDF_tree_rings_TMAX_extended`).
Correlations and significance levels for months April-August are given in **APPENDIX**.

<!--MULTIVARIATE ANALYSIS METHODS-->
We used a multivariate model to test for joint effects of April and summer $T_{max}$ on RWI.
We began by testing univariate correlations of $T_{max}$ over three summer windows: June, June-July, and May-August. 
Having determined that, among these, June-July explained the most variation, we then analyzed the joint effects of April $T_{max}$ and June-July $T_{max}$ on RWI for each chronology independently using the base lm() function in R. 
Slopes and p-values for each chronology are given in **APPENDIX**.

>>>>

![**Figure 3 | Sensitivity of annual growth, as derived from tree-rings, to monthly maximum temperatures, for `r n_chronologies` chronologies from `r n_cores_sites` sites across eastern North America** (`r EDF_map `). Chronologies are grouped by xylem porosity and ordered by mean maximum April temperature. Chronology details are given in `r chron_table`.](tables_figures/tree_rings_tmax.png){ width=100% }

@@

<!--QUILT PLOT METHODS-->
Correlations between monthly climate and $RWI$ were assessed using ‘dplR’[@bunn_dendrochronology_2008] and ‘bootRes’[@zang_dendroclimatic_2013] in R v.1.3.1093 (R Core Team, 2020), which correlated functions and bootstrapped confidence intervals for these relationships[@biondi_dendroclim2002_2004].
We analyzed these correlations for January through September of the current year (presented in Fig. `r tree_rings`, `r EDF_tree_rings_TMIN`).
To test for potential lag effects effects of spring temperatures on the following year's growth, we also ran a version of the analysis extending back to include climate of every month of the previous year (`r EDF_tree_rings_TMAX_extended`).
Correlations and significance levels for months April-August are given in `r chron_table`.

<!--MULTIVARIATE ANALYSIS METHODS-->
We used a multivariate model to test for joint effects of April and summer $T_{max}$ on RWI.
We began by testing univariate correlations of $T_{max}$ over three summer windows: June, June-July, and May-August. 
Having determined that, among these, June-July explained the most variation, we then analyzed the joint effects of April $T_{max}$ and June-July $T_{max}$ on RWI for each chronology independently using the base lm() function in R. 
Slopes and p-values for each chronology are given in `r chron_table`.
